Data Prep

### 2024-02-06 scripts/00.0_dataPrep.qmd
updated file path to use here::here
re-did subsampling for movement data, and added subsampling for social data too

```{r}
base::load("movebankCredentials/pw.Rda")
MB.LoginObject <- move::movebankLogin(username = "kaijagahm", password = pw)
rm(pw)
```

@@

```{r}
load("data/dataPrep/cleaned.Rda")
```

@@

@@

```{r}
load("data/dataPrep/with_altitudes.Rda")
load("data/dataPrep/season_names.Rda")
```

@@

# Function to downsample the data
subsample <- function(df, idCol = "Nili_id", 
                      timestampCol = "timestamp", mins = 10){
  sub <- df %>%
    arrange(idCol, timestampCol) %>%
    group_by(.data[[idCol]]) %>%
    mutate(tc = cut(.data[[timestampCol]], 
                    breaks = paste(as.character(mins), "min", sep = " "))) %>%
    group_by(.data[[idCol]], 
             "d" = lubridate::date(.data[[timestampCol]]), tc) %>%
    slice(1) %>%
    ungroup() %>%
    dplyr::select(-c("d", "tc"))
  return(sub)
}

@@

save(downsampled_10min, file = "data/dataPrep/downsampled_10min.Rda")

>>>>

```{r}
base::load("movebankCredentials", "pw.Rda")
MB.LoginObject <- move::movebankLogin(username = "kaijagahm", password = pw)
rm(pw)
```

@@

```{r}
load(here::here("data", "dataPrep", "cleaned.Rda"))
```

@@

```{r}
load(here::here("data", "dataPrep", "removed_lfr.Rda"))
```

# Function to downsample the data
subsample <- function(df, idCol = "Nili_id", 
                      timestampCol = "timestamp", mins = 10){
  sub <- df %>%
    mutate(d = lubridate::date(.data[[timestampCol]])) %>% 
    group_by(.data[[idCol]]) %>%
    arrange(timestampCol, .by_group = T) %>%
    mutate(tc = cut(.data[[timestampCol]], 
                    breaks = paste(as.character(mins), 
                                   "min", sep = " "))) %>%
    ungroup() %>%
    group_by(.data[[idCol]], d, tc) %>%
    slice(1) %>%
    ungroup() %>%
    dplyr::select(-c("d", "tc"))
  return(sub)
}

downsampled_10min_forSocial <- map(removed_lfr, ~subsample(df = .x, idCol = "Nili_id", timestampCol = "timestamp", mins = 10), .progress = T)

# Add information on # of days tracked for each individual
downsampled_10min_forSocial <- map(downsampled_10min_forSocial, ~.x %>% group_by(Nili_id) %>% 
                       mutate(daysTracked = length(unique(dateOnly))))
save(downsampled_10min_forSocial, file = here::here("data", "dataPrep", "downsampled_10min_forSocial.Rda"))

map_dbl(removed_lfr, nrow) %>% setNames(season_names)
map_dbl(downsampled_10min_forSocial, nrow) %>% setNames(season_names)

# tidying
rm(removed_lfr)
rm(downsampled_10min_forSocial)
gc()
```

@@

```{r}
load(here::here("data", "dataPrep", "with_altitudes.Rda"))
load(here::here("data", "dataPrep", "season_names.Rda"))
```

@@

# defined the "subsample" function previously above

@@

save(downsampled_10min, file = here::here("data", "dataPrep", "downsampled_10min.Rda"))
